% This is lnbip.tex the demonstration file of the LaTeX macro package for
% Lecture Notes in Business Information Processing from Springer-Verlag.
% It serves as a template for authors as well.
% version 1.0 for LaTeX2e
%
\documentclass[lnbip]{svmultln}
%
\usepackage{makeidx}  % allows for indexgeneration
% \makeindex          % be prepared for an author index
%
\usepackage{graphics}
\usepackage{graphicx}
\begin{document}
%
\mainmatter              % start of the contribution
%
\title{An Multi Agent System for Argumentation}
\subtitle{Research Report}
%
\titlerunning{Argumentation MAS}  
% abbreviated title (for running head)
% also used for the TOC unless
% \toctitle is used
%
\author{Alexandru Sorici \and Alin Danciu \and Tudor Berariu}
%
\authorrunning{A. Sorici, A. Danciu, T. Berariu}
% abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Alexandru Sorici, Alin Danciu, Tudor Berariu}
%
\institute{Faculty of Automatic Control and Computer Science, \\ University "Politehnica" of Bucharest, Romania}

\maketitle              % typeset the title of the contribution

\begin{abstract}        % give a summary of your paper
In this research report we present a framework for argumentation in multi agent systems with natural language features that supports interaction with human agents. The system uses the AIF ontology and each agent may specialize in one or more domains using one or more domain specific ontologies.
% please supply keywords within your abstract
\keywords {natural language processing, machine learning, argumentation, statistical learning, multi agent system}
\end{abstract}
%
\include{chap1}
\include{chap3}
\include{chap2}

\newpage
\begin{thebibliography}{5}

\bibitem{steg1}Karsten Stegmann, Armin Weinberger and Frank Fischer: Facilitating argumentative knowledge construction with computer-supported collaboration scripts. International Journal of Computer-Supported Collaborative Learning, Vol. 2, No. 4, Springer New York

\bibitem{palau1}Raquel Mochales Palau and Marie-Francine Moens: Argumentation Mining: The Detection, Classification and Structuring of Arguments in Text.  	 International Conference on Artificial Intelligence and Law, 2009.

\bibitem{palau2}Raquel Mochales Palau and Marie-Francine Moens :Study on the Structure of Argumentation in Case Law.Proceeding of the 2008 conference on Legal Knowledge and Information Systems, 2008.

\bibitem{safia}Safia ABBAS, Hajime SAWAMURA: ALES: An Innovative Argument Learning Environment, Proceedings of the 17th International Conference on Computers in Education, 2009.

\bibitem{araucaria}Chris Reed, Raquel Mochales Palau, Glenn Rowe and Marie-Francine Moens: Language Resources for Studying Argument.The International Conference on Language Resources and Evaluation, 2008.

\bibitem{echr}Raquel Mochales Palau and Aagje Ieven: Creating an argumentation corpus: do theories apply to real arguments?Proceedings of the 12th International Conference on Artificial Intelligence and Law, 2009.

\bibitem{ara1}Glenn Rowe, Fabrizio Macagno, Chris Reed and Douglas Walton: Araucaria as a Tool for Diagramming Arguments in Teaching and Studying Philosophy, 2009.

\bibitem{doug}Douglas Walton: Argumentation Theory: A Very Short Introduction. 	Argumentation in Artificial Intelligence, Springer US, 2009.

\bibitem{amgoud}Amgoud L., Maudet N. and Parsons S.: Modeling dialogues using argumentation. Proceedings. Fourth International Conference on Multi Agent Systems, 2000.

\bibitem{parsons}Parsons S., Sierra C. and Jennings N.:Agents that reason and negotiate by arguing.Journal of Logic and Computation, 1998

\bibitem{reed}Chris Reed and Doug Walton: Towards a Formal and Implemented Model of Argumentation Schemes in Agent Communication. Lecture Notes in Computer Science, Springer Berlin / Heidelberg, 2005

\bibitem{kiss}Kiss Tibor and Strunk Jan: Unsupervised Multilingual Sentence Boundary Detection.Computational Linguistics 32: 485-525,2006.

\bibitem{reed1}C. Reed and G. Rowe: Araucaria: Software for argument analysis, diagramming and representation.International Journal of AI Tools, 14(3-4):961{980, 2004}.

\bibitem{aif}Carlos Chesnevar, Jarred McGinnis, Sanjay Modgil, Iyad Rahwan, Chris Reed, Guillermo Simari, Matthew South, Gerard Vreeswijk and Steven Willmott: Towards an Argument Interchange Format.The Knowledge Engineering Review, pages 1-25, 2007.

\bibitem{dung}Phan Minh Dung: ON THE ACCEPTABILITY OF ARGUMENTS AND ITS FUNDAMENTAL ROLE IN NONMONOTONIC REASONING, LOGIC PROGRAMMING AND N-PERSONS GAMES, Asian Institute of Technology.

\bibitem{amg}L. Amgoud, C. Devred, and M.C. Lagasquie-Schiex.A constrained argumentation system for practical reasoning.Argumentation in Multi-Agent Systems, pages 37{56, 2009}.

\bibitem{amg1}L. Amgoud, N. Maudet, and S. Parsons. Modeling dialogues using argumentation.In Multi Agent Systems, 2000. Proceedings. Fourth International Conference on, pages 31{38, 2000}.

\bibitem{jiang}J. Jiang and D. Conrath.Semantic similarity based on corpus statistics and lexical taxonomy. Proceedings on International Conference on Research in Computational Linguistics, pages 19{33, 1997. Taiwan}.

\bibitem{lin}D. Lin. An information-theoretic definition of similarity. Proceedings of the International Conference on Machine Learning, Madison, August 1998.

\bibitem{mod}S. Modgil and M. Luck. Argumentation based resolution of conflicts between desires and normative goals. Argumentation in Multi-Agent Systems, pages 19{36,2009}.

\end{thebibliography}

\end{document}
